T-reX: A tool to quantify waste and material footprints in current and future Life Cycle Assessment (LCA) databases

### 2024-03-15 latex_files/main.tex
update

        A case study of five Li-ion batteries demonstrated T-reX's utility, quantifying categorised waste and material inventory footprints, and thus, their potential environmental burdens. T-reX can aid sustainable decision-making and contribute to the development of the `circular economy' by facilitating analysis of material consumption and waste generation in LCA.

@@

% list of abbreviations
\begin{table}[H]
    \centering
    \caption{List of abbreviations}
    \label{tab:abbreviations}
    \begin{tabular}{ll}
    \toprule
    CF & Carbon Footprint \\
    EF & Ecological Footprint \\
    CML & Centrum voor Milieuwetenschappen (Centre for Environmental Science) \\
    CRM & Critical Raw Material \\
    CPC & Cooperative Patent Classification \\
    CSI & Crustal Scarcity Indicator \\
    CSP & Crustal Scarcity Potential \\
    EDIP & Environmental Design of Industrial Products \\
    EOL & End-of-Life \\
    FOEN & Swiss Federal Office for the Environment \\
    IAM & Integrated Assessment Model \\
    LCA & Life Cycle Assessment \\
    LCI & Life Cycle Inventory \\
    LCIA & Life Cycle Impact Assessment \\
    LFP & Lithium Iron Phosphate \\
    LiMn$_2$O$_4$ & Lithium Manganese Oxide \\
    MF & Material Footprint \\
    NCA & Nickel Cobalt Aluminum \\
    NMC & Nickel Manganese Cobalt \\
    PWF & Product Waste Footprint \\
    RCP & Representative Concentration Pathway \\
    ReCiPe & A standard LCIA method set \\
    SSPs & Shared Socioeconomic Pathways \\
    UBP & Umweltbelastungspünkte (Environmental Impact Points) \\
    WF & Waste Footprint \\
    \bottomrule
    \end{tabular}
    \end{table}

@@

>>>>

        A case study of five lithium ion batteries demonstrated T-reX's utility, quantifying categorised waste and material inventory footprints, and thus, their potential environmental burdens. T-reX can aid sustainable decision-making and contribute to the development of the `circular economy' by facilitating analysis of material consumption and waste generation in LCA.

@@

% list of abbreviations
\begin{table}[H]
    \centering
    \caption{List of abbreviations}
    \label{tab:abbreviations}
    \begin{tabular}{ll}
    \toprule
    CF & Carbon Footprint \\
    EF & Ecological Footprint \\
    CML & Centrum voor Milieuwetenschappen (Centre for Environmental Science) \\
    CRM & Critical Raw Material \\
    CPC & Cooperative Patent Classification \\
    CSI & Crustal Scarcity Indicator \\
    CSP & Crustal Scarcity Potential \\
    EDIP & Environmental Design of Industrial Products \\
    EOL & End-of-Life \\
    FOEN & Swiss Federal Office for the Environment \\
    IAM & Integrated Assessment Model \\
    LCA & Life Cycle Assessment \\
    LCI & Life Cycle Inventory \\
    LCIA & Life Cycle Impact Assessment \\
    LFP & Lithium Iron Phosphate \\
    Li-ion & Lithium ion \\
    LiMn$_2$O$_4$ & Lithium Manganese Oxide \\
    MF & Material Footprint \\
    NCA & Nickel Cobalt Aluminum \\
    NMC & Nickel Manganese Cobalt \\
    PWF & Product Waste Footprint \\
    RCP & Representative Concentration Pathway \\
    ReCiPe & A standard LCIA method set \\
    SSPs & Shared Socioeconomic Pathways \\
    UBP & Umweltbelastungspünkte (Environmental Impact Points) \\
    WF & Waste Footprint \\
    \bottomrule
    \end{tabular}
    \end{table}

@@

The authors would like to acknowledge XXXX, XXXX, XXXX, XXX, who were part of the futures thinking small group session at the FutuRaM consortium meeting in Berlin in June 2023 in which the term `T-reX/T(ool)-reX' was coined to name the vision presented by Stewart Charles McDowall of a comprehensive opensource software framework for the study and development of secondary raw material systems. The authors hope to continue the development of T-reX toward this vision.
